Exploitation Techniques and Mitigations

### 2016-01-26 docs/paper.tex
Paper: Draft other architectures

\section{Platform x86}

@@

>>>>

\section{Platform x86}
\label{sec:x86}

@@

We have already reasoned about why x86 was the platform chosen for all this in
\cref{sec:x86}, but now we'll have a short look at two other common platforms.
Most of this is directly taken from \cite{rpisec} with some smaller additions.

On x86 instructions range from \SIrange{1}{15}{\byte} and one can even bend the
instruction pointer between instructions to yield a completely different
execution than originally available.

\subsection{x86\_64}

x86\_64, also known as x64 and AMD64, is at its core a \SI{64}{\bit} extension
to x86 which already replaced a lot of x86 machines. Its general purpose
registers are \SI{64}{\bit} wide and there are eight more of them.

We will find the most interesting difference in the calling convention,
\textit{fastcall}, where (the first few) arguments are passed via registers
instead of pushing them onto the stack. This makes ROP much easier.

Contrary, breaking ASLR gets much harder since the address space is \emph{much}
bigger which yields more entropy for the randomization. This renders brute
force (and heap spraying) basically useless, but we can still resort to the
info leak. Breaking a canary via brute force gets only a little bit harder, but
this has already been shown.

\subsection{ARM}

ARM CPUs will be encountered mostly in portable, low-power-oriented devices
such as smart phones and tables, but are also used in embedded devices like
routers. It consists of an \SI{32}{\bit} RISC instruction set with a
\SI{16}{\bit} mode (THUMB). The used calling convention is basically the same
as under x86\_64 (fastcall)

Compared to the previous both, ARM has a \SI{4}{\byte} instruction alignment
--- \SI{2}{\byte} under THUMB.

A heads up about caching: on ARM cache has to be flushed manually (or via large
memory operations).
